[dcpo_demsupport]

### 2020-09-27 paper/dcpo_demsupport.Rmd
plot updated: adding cls uncertainty

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker # visualization
)

# Functions preload
set.seed(313)
```

@@

load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dem_mood_apsr.RData"))

```{r claassenAJPS}
# Pooled model -----

@@

# regime = ifelse(sd2$Regime_VD > 1, 1, 0)

@@

save(df_result_cls, file = here::here("output", "estimates_clsAJPS.RDS"))
```

```{r claassenUncertainty}

ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_claassen <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

df_result_dcpo <- map(mod_ls, estimate_dcpo)

save(df_result_dcpo, file = here::here("output", "estimates_dcpo.RDS"))
```

```{r dcpoPointAJPS}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

reformat_dcpo_output <- function(x, parameter_name) {
  df_temp <- x %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = parameter_name) %>%
    arrange(country, year)
  return(df_temp)
}

@@

load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoMeanAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

@@

df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Democratic\n Mood\n (t-1)",
      "Log GDP\n per capita\n (t−1)",
      "GDP per\n capita Growth\n (t−1)",
      "Regional\n Democracy\n (t−1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n Dependence\n (t−1)"),
    time = 2)
  )

@@

plot_clsVsDCPO <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)")+
  theme(legend.position = "none")

@@

df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Democratic\n Demo Only\n (t-1)",
      "Democratic\n Auto Only\n (t-1)",
      "Log GDP\n per capita\n (t−1)",
      "GDP per\n capita Growth\n (t−1)",
      "Regional\n Democracy\n (t−1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n Dependence\n (t−1)"),
    time = 2)
  )

plot_clsVsDCPO2 <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)")+
  theme(legend.position = "none")

gridExtra::grid.arrange(plot_clsVsDCPO, plot_clsVsDCPO2, ncol = 2)
```

```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}

@@

save(df_result_clsAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
```

```{r dcpoPointAPSR}
df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
  filter(year >= firstyear)

@@

load(here::here("output", "estimates_clsAPSR.RDS"))
load(here::here("output", "estimates_dcpoMeanAPSR.RDS"))

@@

df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)"),
    time = 2)
  )

plot_clsVsDCPO <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Democracy Mood")+
  theme(legend.position = "none")

@@

df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic\n Mood\n (t-1)",
        "Democratic\n Mood\n (t-2)",
      "Liberal\n Democracy\n (Difference)",
      "Liberal\n Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)",
      "Corruption\n (Difference)",
      "Corruption\n (t−1)"
      ),time = 2)
  )

plot_clsVsDCPO2 <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Democracy Mood")+
  theme(legend.position = "none")

gridExtra::grid.arrange(plot_clsVsDCPO, plot_clsVsDCPO2, ncol = 2)
```

```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker # visualization
)

# Functions preload
set.seed(313)

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

# Theme setup
theme_set(theme_minimal())
source("../R/uiowa_palette.R")
```

@@

load(here::here("data", "claassen_replication_input.rda"))
load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dem_mood_apsr.RData"))

@@

reformat_dcpo_output <- function(x, parameter_name) {
  df_temp <- x %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = parameter_name) %>%
    arrange(country, year)
  return(df_temp)
}
```

```{r claassenAJPS}
# Pooled model -----
# regime = ifelse(sd2$Regime_VD > 1, 1, 0)

@@

save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

```{r claassenUncertaintyAJPS,eval=FALSE}

ls_country <- unique(claassen_replication_input$data$country)
first_year <- min(claassen_replication_input$data$year)

sd_control <- sd.plm %>%
  mutate(
    country = as.character(Country),
    year = as.numeric(as.character(Year)),
    regime = ifelse(Regime_VD > 1, 1, 0)
  )

df_cls <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
    #           by = c("year", "country")) %>%
    left_join(sd_control, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

estimate_cls <- function(aModel, aType = "pooling") {
  if (aType == "gmm") {
    result_cls_1k <- map(df_cls, function(aDataset) {
      pgmm(
        as.formula(aModel),
        effect = "individual",
        model = "onestep",
        transformation = "ld",
        indexes = c("Country", "Year"),
        data = aDataset
      )
    })

    result_vars_cls_1k <-
      mitools::MIextract(result_cls_1k, fun = vcovHC_se)

  } else {
    result_cls_1k <- map(df_cls, function(aDataset) {
      plm::plm(aModel,
               model = "pooling",
               data = aDataset)
    })

    result_vars_cls_1k <-
      mitools::MIextract(result_cls_1k, fun = vcovBK_se)
  }

  result_betas_cls_1k <-
    mitools::MIextract(result_cls_1k, fun = coef)

  df_result_cls <-
    summary(
      mitools::MIcombine(results = result_betas_cls_1k, variance = result_vars_cls_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))
}

mod_ls <- paste0(
  "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
)

df_result_clsUncertain <- map(mod_ls, estimate_cls)

save(df_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```

```{r dcpoPointAJPS, eval=FALSE}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

load(here::here("output", "estimates_clsMeanAJPS.RDS"))
load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

@@

df_plot <- df_result_clsUncertain[[1]] %>% 
  mutate(model = "Claassen w. Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAJPS[[1]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Democratic\n Mood\n (t-1)",
      "Log GDP\n per capita\n (t−1)",
      "GDP per\n capita Growth\n (t−1)",
      "Regional\n Democracy\n (t−1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n Dependence\n (t−1)"),
    time = 3)
  )

plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Institutional Democracy (Vdem)",
    subtitle = "Pooled"
  ) +
  theme(legend.position = "none")

@@

@@

df_plot <- df_result_clsUncertain[[2]] %>% 
  mutate(model = "Claassen w. Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAJPS[[2]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Democratic\n Demo Only\n (t-1)",
      "Democratic\n Auto Only\n (t-1)",
      "Log GDP\n per capita\n (t−1)",
      "GDP per\n capita Growth\n (t−1)",
      "Regional\n Democracy\n (t−1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n Dependence\n (t−1)"),
    time = 3)
  )

plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  theme(legend.position = "bottom")

legend <- get_legend(plot_AJPS2)

plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")

grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol=2, nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,3)),
             widths = c(2.7, 2.7), heights = c(2.5, 0.2))

```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty", eval=FALSE}

@@

save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

```{r claassenAPSRUncertainty}
ls_country <- unique(claassen_replication_input$data$country)
first_year <- min(claassen_replication_input$data$year)

sd_control <- sd.plm %>%
  mutate(
    country = as.character(Country),
    year = as.numeric(as.character(Year))
  )

df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
    #           by = c("year", "country")) %>%
    left_join(sd_control, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

estimate_cls <- vector(mode = "list")

estimate_cls[[1]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
      model = "pooling",
      data = aDataset
    )
}

estimate_cls[[2]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
      model = "pooling",
      data = aDataset
    )
}

df_result_clsUncertainAPSR <- map(estimate_cls, function(aModel){
  aFit <- map(df_clsAPSR, aModel)

  result_vars_cls_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
  result_betas_cls_1k <- mitools::MIextract(aFit, fun = coef)

  summary(
      mitools::MIcombine(results = result_betas_cls_1k, 
                         variance = result_vars_cls_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))

save(df_result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
```

```{r dcpoPointAPSR, eval = FALSE}
df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
  filter(year >= firstyear)

@@

load(here::here("output", "estimates_clsMeanAPSR.RDS"))
load(here::here("output", "estimates_clsAPSR.RDS"))
load(here::here("output", "estimates_dcpoAPSR.RDS"))

@@

df_plot <- df_result_clsUncertainAPSR[[1]] %>% 
  mutate(model = "Claassen w. Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAPSR[[1]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)"),
    time = 3)
  )

plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Democratic Mood",
    subtitle = "Basic"
  ) +
  theme(legend.position = "none")

@@

df_plot <- df_result_clsUncertainAPSR[[2]] %>% 
  mutate(model = "Claassen w. Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAPSR[[2]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic\n Mood\n (t-1)",
        "Democratic\n Mood\n (t-2)",
      "Liberal\n Democracy\n (Difference)",
      "Liberal\n Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)",
      "Corruption\n (Difference)",
      "Corruption\n (t−1)"
      ),time = 3)
  )

plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "w. Corruption"
  )

legend <- get_legend(plot_AJPS2)

plot_APSR2 <- plot_APSR2 +
  theme(legend.position = "none")

gridExtra::grid.arrange(plot_APSR1, plot_APSR2, legend, ncol=2, nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,3)),
             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
```

```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", eval = FALSE}
